### 2011-03-04 htdocs/user.tex
Added note on random restart in user.tex
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1291 40876441-3496-0410-a613-a2fca35b2ae2
Shear initialisation comment in user.tex
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1294 40876441-3496-0410-a613-a2fca35b2ae2

@@

>>>>

\subsubsection{Restarting at random!}

Be careful if you are restarting a simulation that used the random
initialisation at $t=0$. You must change to

\texttt{colloid\_init  from\_file}

to avoid generating a completely new set of random positions
(which will not be consistent with the density and order parameter
fields at the restart time). This is almost certainly not what you
intended!

@@

There is a further option for use with the special case in which
top and bottom walls in the $z-direction$ are used to drive a shear
flow (typically with the top speed positive and the bottom speed
negative). The key

\inputkey{boundary\_shear\_init}

may be switched on (set to 1) to provide initialisation of the
LB distributions appropriate for the specified shear rate based
on a linear velocity profile in the $z-$direction. The default
is to initialise the fluid at rest.
